---
title: "LAB"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r, message = FALSE, warning = FALSE}
library(lab)

timeSeriesData <- getTimeSeriesLab(labData = labMIMIC,
                                   idColName = SUBJECT_ID,
                                   labItemColName = ITEMID,
                                   dateColName = CHARTTIME,
                                   valueColName = VALUENUM,
                                   indexDate = first,
                                   gapDate = 360,
                                   completeWindows = TRUE)
head(timeSeriesData)
```
## Including Plots

The plot 

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
