---
title: "LAB"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## lab
# I. Introduction
The proposed open-source lab package is a software tool that help users to explore and process laboratory data in electronic health records (EHRs). With the lab package, researchers can easily map local laboratory codes to the universal standard, mark abnormal results, process general statistical information about longitudinal laboratory data, impute missing values, generate analysis ready data, and visualize these data.

## Feature
- **Data Mapping**   
- **Time Series Overview**
- **Value Imputation**
- **Visualization** 

## Usage

```r
# install.packages("devtools")
devtools::install_github("DHLab-TSENG/lab")
```


```{r, message = FALSE, warning = FALSE}
library(lab)

# Dataset

head(labSample)

head(mapSample)


# I. Data Mapping

loincSample <- mapLOINC(labData = labSample, labItemColName = ITEMID, mappingTable = mapSample)
head(loincSample)

loincMarkedSample <- getAbnormalMark(labData = loincSample, 
                                     idColName = SUBJECT_ID,
                                     labItemColName = LOINC, 
                                     valueColName = VALUENUM, 
                                     genderColName = GENDER,
                                     genderTable = patientSample,
                                     referenceTable = refLOINC)
head(loincMarkedSample)

# II. Time Series Overview

windowProportion <- plotWindowProportion(labData = loincSample, 
                     idColName = SUBJECT_ID, 
                     labItemColName = LOINC, 
                     dateColName = CHARTTIME, 
                     indexDate = first, 
                     gapDate = c(30, 90, 180, 360), 
                     topN = 5)

print(windowProportion$graph)

print(windowProportion$missingData)


timeSeriesData <- getTimeSeriesLab(labData = loincSample,
                                   idColName = SUBJECT_ID,
                                   labItemColName = LOINC + CATEGORY,
                                   dateColName = CHARTTIME,
                                   valueColName = VALUENUM,
                                   indexDate = first,
                                   gapDate = 360,
                                   completeWindows = TRUE)
head(timeSeriesData)

fullTimeSeriesData <- imputeTimeSeriesLab(labData = timeSeriesData,
                                   idColName = ID,
                                   labItemColName = LOINC + CATEGORY,
                                   windowColName = Window,
                                   valueColName = Max & Min & Mean & Nearest,
                                   impMethod = NOCB)
head(fullTimeSeriesData)


```
<!-- ## Visulization -->

<!-- The plot -->

<!-- ```{r pressure, echo=FALSE} -->
<!-- plot(pressure) -->
<!-- ``` -->

